Analysis for Project

### 2021-11-18 analysis/analysis.Rmd
Add description of results for Black/White and Black/Latino respondents

Summarize these results.

>>>>

Ok, let me try to summarize these results, by group.

## Black/White results

For the first three models, the results are pretty consistent. Black/White biracials are much closer to the lower grade retention rates of whites, although they have rates that are clearly still higher than whites. Controlling for parental resources changes things considerably. First, the gap between Blacks and Whites shrinks considerably (visually it looks like its cut about in half). Second, Black/White biracials actually have lower rates than either group. They aren't that different than whites in effect size but the difference is statistically significant.

Why does the big change occur in the parental resources model. The descriptive stat table shows that the family resources of Black/White biracials are closer to those of black students than white students. So, Black/White biracials are at a disadvantage relative to whites, which is controlled for in the last model.

## Black/Latino results

In the crude model, its clear that there isn't much difference in the grade retention rates of Blacks and Latinos, with Blacks having a slightly higher rate than Latinos. The Black/Latino group has rates well below either of these groups. In fact, their grade retention rates in the crude model are closer to Whites.

Interestingly, the fixed effects model reverses the ordering of Blacks and Latinos, but this is then reversed again in the cultural resources model. In addition the gap between Latinos and Blacks grows a little in the cultural resources model, which is expected. In all of these models, the Black/Latino group remains below either of those two groups, although the gap shrinks considerably across models.

Things change quite a bit in the parent resources model. The gap between blacks and Latinos grows and the Black/Latino group now looks almost identical to the Latino group. So, some of their lower rate was due to better family resources, particularly relative to Latinos, as can be seen on the table of descriptive stats.

## Black/Asian results
